Translation Elicitation: Report

### 2022-04-27 docs/index.Rmd

# SD of random effects
post_sd_data <- post_draws 
filter(str_detect(.variable, "sd_")) 
mutate(
  group = case_when(
    str_detect(.variable, "participant") ~ "Participants",
    str_detect(.variable, "word") ~ "Words"
  ),    
  .variable_name = str_remove(
    .variable,
    "sd_participant__|sd_word__"
  ) )
str_replace_all(str_repl) %>% 
  factor(
    levels = c(
      "Intercept", 
      "Frequency\n[+1 SD]",
      "PTHN\n[+1 SD]", 
      "Levenshtein\n[+1 SD]", 
      "PTHN \u00d7 Levenshtein",
      "Group 1\n[cat/spa-ENG vs. cat-SPA]",
      "Group 2\n[cat-ENG vs. spa-ENG]",
      "Levenshtein \u00d7 Group 1",
      "Levenshtein \u00d7 Group 2"
    )
  ),
.value = ifelse(
  str_detect(.variable, "Intercept"), 
  inv_logit_scaled(.value), 
  .value/4
)
)

>>>>

# SD of random effects
post_sd_data <- post_draws 
filter(str_detect(.variable, "sd_")) 
mutate(
    group = case_when(
        str_detect(.variable, "participant") ~ "Participants",
        str_detect(.variable, "word") ~ "Words"
    ),    
    .variable_name = str_remove(
        .variable,
        "sd_participant__|sd_word__"
    ),
    str_replace_all(str_repl) %>% 
        factor(
            levels = c(
                "Intercept", 
                "Frequency\n[+1 SD]",
                "PTHN\n[+1 SD]", 
                "Levenshtein\n[+1 SD]", 
                "PTHN \u00d7 Levenshtein",
                "Group 1\n[cat/spa-ENG vs. cat-SPA]",
                "Group 2\n[cat-ENG vs. spa-ENG]",
                "Levenshtein \u00d7 Group 1",
                "Levenshtein \u00d7 Group 2"
            )
        ),
    .value = ifelse(
        str_detect(.variable, "Intercept"), 
        inv_logit_scaled(.value), 
        .value/4
    )
)
